plyranges: A grammar of genomic data transformation

### 2018-09-20 paper.Rmd
typos

After filtering for regions with a coverage score greater than 8, we can
reduce individual runs to ranges representing the islands of coverage by
using the `reduce_ranges()` function. This function allows a summary
to be computer over each island: in this case we take the maximum of 
the scores to find the coverage peaks over chromosome 10.

@@

```{r, cache = TRUE}
alignments <- h1_bam_sorted %>% 
  read_bam() %>%
  filter_by_overlaps(locations) %>%
  select(seq) %>%
  mutate(score = as.numeric(letterFrequency(seq, "GC", as.prob = TRUE))) %>% 
  select(score)
alignments
```

@@

```{r, cache = TRUE}
ti_tv_results <- h1_snp_array %>% 
  group_by(seqnames) %>%
  summarize(n_snps = n(),
            ti_tv = sum(transition) / sum(!transition)) 
```

>>>>

We then filter for regions with a coverage score greater than 8, and following
this reduce individual runs to ranges representing the islands of coverage.
This is achieved with the `reduce_ranges()` function, which allows a summary
to be computed over each island: in this case we take the maximum of 
the scores to find the coverage peaks over chromosome 10.

@@

```{r, cache = TRUE}
alignments <- h1_bam_sorted %>% 
  read_bam() %>%
  filter_by_overlaps(locations) %>%
  select(seq) %>%
  mutate(
    score = as.numeric(letterFrequency(seq, "GC", as.prob = TRUE))
  ) %>% 
  select(score)
alignments
```

@@

```{r, cache = TRUE}
ti_tv_results <- h1_snp_array %>% 
  group_by(seqnames) %>%
  summarize(n_snps = n(),
            ti_tv = sum(transition) / sum(!transition)) 
ti_tv_results
```
